Suplementary Material 3: Run Simulations on the Last Birth Omited Data

### 2023-04-04 S3_run_simulations_EE_not_last.Rmd
remove population from default fits

## Expand the birth level data for the fit of statistical models:
data_births_monthly_EE <- twinR::expand_data(data_births_monthly_EE)

@@

## Expand the birth level data for the fit of statistical models:
data_births_monthly <- twinR::expand_data(data_births_monthly)

@@

scenarios_to_do <- c("base_model", "P", "I", "S", "H",
                     "PI", "PS", "PH", "IS", "IH", "SH",
                     "PIS", "PIH", "PSH", "ISH", "PISH")
```

@@

```{r make directories}
expName <- "_orig_nl"
slopeDir <- paste0(baseSlopeDir, expName)
fitDir <- paste0(baseFitDir, expName)

@@

data_births_monthly <- data_births_monthly_not_last

>>>>

@@

@@

scenarios_to_do <- c("base_model", "P", "I", "S", "H",
                     "PI", "PS", "PH", "IS", "IH", "SH",
                     "PIS", "PIH", "PSH", "ISH", "PISH")
```
```{r}
#use models without populations predictor
source("./R/twinR_models.R")
```

@@

```{r make directories}
expName <- "_EE_nl"
slopeDir <- paste0(baseSlopeDir, expName)
fitDir <- paste0(baseFitDir, expName)

@@

data_births_monthly <- data_births_monthly_EE_not_last
